The Effect of Different Writing Tasks on Linguistic Style:\\ A Case Study of the ROC Story Cloze Task

### 2017-01-29 docs/language_constraint.tex

\newcommand{\ms}[1]{{\color{cyan}\{\textit{#1}\}$_{ms}$}}
\newcommand{\roy}[1]{\footnote{\color{red}{\textbf{Roy: #1}}}}
\newcommand{\royb}[2]{{\color{red}{\sout{#1}}}{\color{green}{#2}}}
\newcommand{\royc}[3]{\royb{#1}{#2}\roy{#3}}

@@

\begin{document}
\maketitle
\begin{abstract}
People's writing style %is affected by many factors, including topics, sentiment, and individual personality. 
depends on both personal factors such as demographic background and situational factors such as the purpose of writing.
%In this paper we show that engaging authors in different  writing tasks results in them adopting different writing styles.
In this paper, we show that authors adopt different writing style even when engaged with similar tasks if their purpose differs.
%As a case study, we experiment with a recently published machine reading task: 
We present a case study based on 
the {\it story cloze task} \cite{Mostafazadeh:2016}, %.
%In this task, annotators were asked to generate two sentences: one which makes sense given a previous paragraph and another which doesn't.
where people were asked to write two contrastive sentences as story ending: one plausible and one implausible for a given story context. 
%We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
We show that a simple linear classifier with stylistic features obtains 
state-of-the-art results on the task,
substantially higher than sophisticated deep learning models,
even without looking at the story context. 
%Importantly, our model doesn't even look at the previous paragraph, just the two candidate sentences, which, out of context, differ only in the writing task presented to the authors. 
Our results indicate that different tasks dramatically affect the way people write. 
They also provide important lessons for designing new NLP tasks.

@@

\section{Introduction}
Writing style is defined as the the author's choice of words, spelling, grammar and punctuation.\footnote{\url{https://en.wikipedia.org/wiki/Writing_style}}
It is often affected by inter-writer factors such as age \cite{Schler:2006}, gender \cite{Argamon:2003} or mere personality \cite{Stamatatos:2009}, but also by other parameters such as the sentiment of the text \cite{Davidov:2010}, its level of sarcasm \cite{Tsur:2010} and whether it's deceptive \cite{Feng:2012}.  
In this paper we study to what extent is writing style affected by more intricate factors, such as the nature of the writing task.

\begin{table}[!t]
%\small
\begin{tabular}{|p{1.3cm}|p{5.6cm}|} \hline
{\bf Type} & {\bf Example} \\ \hline
{\color{blue}{\it Original}} story & My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	{\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
{\color{forestgreen}{\it Correct}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{forestgreen}{She felt buyer's remorse after the purchase.}} \\ \hline
{\color{red}{\it Wrong}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
\end{tabular}
\caption{\label{ROC-example}}
Examples of stories from the story cloze task. The first row shows an {\it original} story written by one author. 
The second and third row show two endings of the same story: a {\it correct} ending and a {\it wrong} one.
%\end{center}
\end{table}

As a testbed, we experiment with the story cloze task \cite{Mostafazadeh:2016}. 
In this task, authors were asked to write five-sentence self-contained stories (henceforth {\it original} stories).
Following, the stories were given to other authors, who were shown only the first four sentences of each story, 
and were asked to write two one-sentence endings: a {\it correct} ending, and a {\it wrong} ending.
The goal of the task is to determine which of the endings is the correct one.
\tabref{ROC-example} shows an example of an {\it original} story, a {\it correct} story and a {\it wrong} story.

Interestingly, although originally intended to be a machine reading task, the compilation of this task raises several research questions which seem to differ from the original intent of the designers.
First, do authors use different style when asked to write a {\it correct} sentence, compared to a {\it wrong} sentence?
Second, do authors use different style when writing the ending as part of their own five sentence story, compared to reading four sentences, and then writing a standalone ({\it correct}) ending?

Our experiments indicate that the answer to both questions is positive. 
We train a linear classifier, using simple stylistic features, such as sentence length, character n-grams and word n-grams. 
First, we show that on a balanced dataset (chance level is 50\%) our classifier distinguishes between {\it correct} and {\it wrong} endings in 64.5\% of the cases. 
%It is also trained on a set of positive samples and a set of negative ones, rather than pairs of (positive, negative) pairs, as in the original story cloze task.
Second, when trained to distinguish between {\it original} endings and new ({\it correct}) endings, the classifier obtains 68.5\% accuracy. 
Importantly, in both experiments, the classifier uses {\bf only} the last sentence of each of the stories, and does not consider the first four sentences.

In order to further estimate the quality of our results, we turn back to the story cloze task.
Adapting our classifier to the task, we obtain 72.4\% accuracy, a 12.5\% improvement compared to the published state-of-the-art results \cite{Salle:2016}.\footnote{Recently, a shared task for the story cloze task has been published (\url{https://competitions.codalab.org/competitions/15333}). 
At the time of submission, the leading results was 71.1\%, which is  closer to our results, although still inferior.
No details about the validity of this result or the methods used to generate it are available.}
When analyzing the results of our classifier, we see that sentiment plays a significant role in its success,
which suggests that constraining authors to ``wrong'' sentences results in negative text.

We show that the style differences captured by our model can be combined with a state-of-the-art machine reading tool, for which this task was designed, in order to get increased performance on the story cloze task.  
We train a neural language model on the {\it original} five sentence training corpus, and then compute the language probability of each of the candidate endings. 
We add the resulting probabilities as features in our linear classifier, and get an additional 2.8\% improvement -- 75.2\% -- which is 15.3\% better than the best published result.
%For instance, one of the key features for distinguishing between correct and wrong sentences is the over-representation of the word ``hate" in the latter.

\com{Our results suggest that writing style is affected by the the writer's state of mind.
Writing a sentence intended to be {\it wrong} turns out quite differently than a sentence intended to be {\it correct}. 
Similarly, writing a sentence as part of the story is different from reading a story, and then writing the final sentence.}

Our results may have a wide impact on a range of fields. 
First, they have the potential to shed light on cognitive processes that take place in the brain during writing.
%Second, our results might have a more practical value in an era when fake news are becoming prominent,
%as they suggest that these might have different style compared to real news.
Second, the results presented here also provide valuable lessons for designing new NLP tasks,
both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
%Although \cite{Mostafazadeh:2016} seem to have put a lot of effort into designing the task, 
%addressing many potential methodological flaws (see \secref{ROC_Story}), the importance of a few allegedly minor details were underestimated. 
%We show that these details are actually very significant.

The remainder of this paper is organized as follows. In \secref{ROC_Story} we introduce the cloze story task.
We present our model, our experiments and our resutls in sections \ref{ssec:Model}, \ref{ssec:Experiments} and \ref{ssec:Results} respectively.
Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present an ablation study and a discussion, while \secref{Related}  surveys related work. 
We conclude at \secref{Conclusion}.

\isection{The Cloze Story Task}{ROC_Story}
In this paper, we seek to understand how different writing tasks affect writing style.
To do so, we focus on the \textit{Story Cloze Task} \cite{Mostafazadeh:2016}. 
While this task was developed to facilitate representation and learning of commonsense knowledge,
it introduces a few interesting properties which makes it ideal for our purpose. 
We describe the task below.

@@

The ROC Story Corpus consists of 49,255 five-sentence commonsense stories, collected on Amazon Mechanical Turk (AMT).\footnote{Recently, an additional 53K stories were released, which results in roughly 100K stories.}
Workers were instructed to write a coherent story, which has a clear beginning and end. 
To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories,
which resulted in a wide range of different topics.

\paragraph{Story Cloze Task.}
After compiling the story corpus, the {\it Story Cloze Task} -- a task based on the corpus -- was introduced.
A subset of the stories was selected, and the first four sentences of each story were presented to AMT workers.
Workers were asked to write a {\it correct} and a {\it wrong} ending to each story prefix. 
Both endings had to complete the story using one of the characters in it.
Importantly,  when read out of context, the ending had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.

The resulting stories, both {\it correct} and {\it wrong}, were then individually rated for coherence and meaningfulness. 
Only stories rated as simultaneously coherent with a {\it correct} ending and neutral with a {\it wrong} ending were selected for the task. 
It is worth noting that workers rated the stories as a whole, not only the endings.

Based on the new stories, \citet{Mostafazadeh:2016} proposed the {\it Story Cloze Task}. 
The task is simple -- given a pair of stories that differ only in their endings, the system is required to determine which ending is {\it correct} and which is {\it wrong}.
The authors published the ROC story corpus as the training data, and the task composed of development and test sets for which both {\it correct} and {\it wrong} endings are found.
The task was suggested as an extensive evaluation framework:
as a machine reading task, as the shared task for the  Linking Models of Lexical, Sentential and Discourse-level Semantics workshop (LSDSem 2017), and as a testbed for vector-space evaluation \cite{mostafazadeh2016story}.

\paragraph{State-of-the-Art Performance.}
Interestingly, at the time of submission, 10 months after the paper was first published, the published benchmark on this task is still below 60\% \cite{Salle:2016}.\footnote{The LSDSem`17 shared task website does report higher results (71.1\%), which are still unpublished.}
This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SQuAD \cite{rajpurkar2016squad} and SNLI \cite{bowman2015large}, for which results improved dramatically over a similar period of time.
This suggest that this task is challenging and that high performance is hard to achieve.

@@

Despite these efforts, several key aspects were not controlled for. 
First, the training set for the task (ROC Stories corpus) is not really a training set, as it contains only positive ({\it correct}) samples, and not negative ({\it wrong}) ones. 
On top of that, the {\it original} endings, which serve as positive training samples, were generated differently from the {\it correct} samples, which serve as the positive samples in the development and test sets. 
While the former are part of a single coherent story written by the same author, the latter were generated by letting an author read four sentences, 
and then asking her to generate a fifth {\it correct} ending. 
This raises the question of whether these different writing setups impose different writing styles. 
We show that this is indeed the case.

Second, although the {\it correct} and {\it wrong} sentences were generated by the same author, 
the tasks for generating them were quite different: in one case, the author was asked to write a {\it correct} ending, which would create a coherent five-sentence story along with the other four sentences. In the other case, the author was asked to write a {\it wrong} ending, which would result in an incoherent five-sentence story. 
In this work, we show that these differences are significant and impose different writing styles on authors.

\paragraph{Initial Analysis.}
We computed several characteristics of the three types of endings: {\it original} endings (from the ROC Story Corpus training set), {\it correct} endings and {\it wrong} endings (both from the story cloze task development set).
Our analysis  reveals several style differences between the different groups. 
First, {\it original} endings are on average much longer (11 words per sentence) than {\it correct} endings (8.75 words), which are in turn also longer (though not as much)  than {\it wrong} ones (8.47 words).
Second, \figref{roc_pos_distribution} shows the distribution of five frequent PoS tags in all three groups. 
The figure shows that both {\it original} and {\it correct} endings use pronouns more frequently than {\it wrong} endings,
which in turn prefer proper nouns, especially compared to {\it original} endings.

Finally, \figref{roc_word_distribution} presents the distribution of five frequent words across the different groups. 
The figure shows that {\it original} endings prefer to use coordinations (``and'') more than  {\it correct} endings, and substantially more than {\it wrong} ones.
Furthermore, {\it original} and {\it correct} endings seem to prefer positive words (e.g., ``better''), while {\it wrong} endings prefer negative ones (``hates'').
Next we show that these style differences are not anecdotic, but can be used to distinguish between the different groups of text.

@@

\begin{figure*}[t!]
\begin{subfigure}{.5\textwidth}
\begin{tikzpicture}
\small
    \begin{axis}[
        width  = 0.4*\textwidth,
        height = 4cm,
      %  major x tick style = transparent,
        ybar=\pgflinewidth,
        x=2.5cm,
       bar width=5pt,
        ymajorgrids = true,
        ylabel = {Frequency in Corpus (\%)},
        symbolic x coords={{\it Original}, {\it Correct}, {\it Wrong}},
        xtick = data,
        scaled y ticks = false,
        %enlarge x limits=0.25,
        ymin=3,
        legend cell align=left,
        legend style={
        		legend columns=-1,
                at={(1,1.05)},
                anchor=south east,
                column sep=1ex
        }
    ]
        \addplot[style={bblue,fill=bblue,mark=none}]
            coordinates {({\it Original}, 15.3) ({\it Correct}, 15.7) ({\it Wrong}, 16.3)};

        \addplot[style={rred,fill=rred,mark=none}]
            coordinates {({\it Original}, 13.4) ({\it Correct}, 15.8) ({\it Wrong}, 15.1)};

        \addplot[style={ggreen,fill=ggreen,mark=none}]
            coordinates {({\it Original}, 10.1) ({\it Correct}, 9.7) ({\it Wrong}, 7.4)};

        \addplot[style={brown,fill=brown,mark=none}]
            coordinates {({\it Original}, 9.1) ({\it Correct}, 9.7) ({\it Wrong}, 9.4)};

        \addplot[style={gray,fill=gray,mark=none}]
            coordinates {({\it Original}, 4.7) ({\it Correct}, 8.3) ({\it Wrong}, 9.5)};

        \legend{NN, VBD, PRP, DT, NNP}
    \end{axis}
\end{tikzpicture}
\caption{\label{roc_pos_distribution}PoS tags}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
\begin{tikzpicture}
\small
    \begin{axis}[
        width  = 0.4*\textwidth,
        height = 4cm,
      %  major x tick style = transparent,
        ybar=\pgflinewidth,
        x=2.5cm,
       bar width=5pt,
        ymajorgrids = true,
%        ylabel = {Frequency in Corpus (\%)},
        symbolic x coords={{\it Original}, {\it Correct}, {\it Wrong}},
        xtick = data,
        scaled y ticks = false,
        %enlarge x limits=0.25,
        ymin=0,
        legend cell align=left,
        legend style={
        		legend columns=-1,
                at={(1,1.05)},
                anchor=south east,
                column sep=1ex
        }
    ]
        \addplot[style={bblue,fill=bblue,mark=none}]
            coordinates {({\it Original}, 3.4) ({\it Correct}, 3.9) ({\it Wrong}, 4)};

        \addplot[style={rred,fill=rred,mark=none}]
            coordinates {({\it Original}, 2.8) ({\it Correct}, 2) ({\it Wrong}, 1.5)};

        \addplot[style={ggreen,fill=ggreen,mark=none}]
            coordinates {({\it Original}, 1.1) ({\it Correct}, 1.4) ({\it Wrong}, 1.6)};

        \addplot[style={brown,fill=brown,mark=none}]
            coordinates {({\it Original}, 0) ({\it Correct}, 0) ({\it Wrong}, 0.7)};

        \addplot[style={gray,fill=gray,mark=none}]
            coordinates {({\it Original}, 0.1) ({\it Correct}, 0.2) ({\it Wrong}, 0)};

        \legend{to, and, I, hates, better}
    \end{axis}
\end{tikzpicture}
\caption{\label{roc_word_distribution}Words}
\end{subfigure}
\caption{The distribution of five frequent PoS tags (\ref{roc_pos_distribution}) and words (\ref{roc_word_distribution})  across different endings: {\it Original} -- endings of stories from the ROC story corpus (the story cloze training set). {\it Correct} -- correct endings, {\it Wrong} -- wrong endings (both from story cloze task).}

@@

The goal of this paper is to determine to what extent does constraining authors in their writing assignments lead to them adopting different writing styles. 
In order to answer these questions, we use simple, classic NLP tools, which have been shown to be very effective for recognizing style (see \secref{Related}).
We describe our model below.

@@

\isectionb{Experiments}
We design two experiments to answer our research questions. 
The first is an attempt to distinguish between {\it correct} and {\it wrong} endings.
The second attempts to distinguish between {\it original} endings and new ({\it correct}) endings.
We describe both experiments below.

>>>>

\newcommand{\ms}[1]{{\color{cyan}\{\textit{#1}\}$_{ms}$}}
\newcommand{\roy}[1]{\footnote{\color{red}{\textbf{Roy: #1}}}}
\newcommand{\royb}[2]{{\color{red}{\sout{#1}}}{\color{green}{#2}}}
\newcommand{\royc}[3]{\royb{#1}{#2}\roy{#3}}
\newcommand{\yc}[1]{{\color{bblue}\{\textit{#1}\}$_{yc}$}}

@@

\begin{document}
\maketitle
\begin{abstract}
%People's writing style is affected by many factors, including topics, sentiment, and individual personality. 
People's writing style depends not just on the authors' personal traits but also on the intent and the cognitive states of the authors. 
%In this paper we show that engaging authors in different  writing tasks results in them adopting different writing styles.
In this paper, we show how similar writing tasks involving different cognitive processes can lead to measurable differences in people's writing style. % of the same authors.  
%As a case study, we experiment with a recently published machine reading task: 
We present a case study based on 
the  {\it story cloze task} \cite{Mostafazadeh:2016}, %.
%In this task, annotators were asked to generate two sentences: one which makes sense given a previous paragraph and another which doesn't.
where annotators were assigned with similar writing tasks with different constraints: (1) writing an entire story on their own vs. adding only a story ending for a given story context and (2) writing a story ending that makes the overall story coherent vs. incoherent. 
%We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
We show that a simple linear classifier informed with stylistic features obtains 
state-of-the-art results on the story cloze challenge,
substantially higher than sophisticated deep learning models,
even without looking at the story context. 
%Importantly, our model doesn't even look at the previous paragraph, just the two candidate sentences, which, out of context, differ only in the writing task presented to the authors. 
Our results demonstrate that different task framings can dramatically affect the way people write. 
They also provide important lessons for designing new NLP tasks.

@@

\section{Introduction}
Writing style is 
%defined as the the author's choice of words, spelling, grammar and punctuation.\footnote{\url{https://en.wikipedia.org/wiki/Writing_style}}
expressed through a range of linguistic elements such as words, sentence structure, and rhetorical devices.
%It is often affected by inter-writer 
It is influenced by both 
personal 
factors such as age \cite{Schler:2006}, gender \cite{Argamon:2003} 
%or mere 
and 
personality \cite{Stamatatos:2009}, 
%but also by other parameters 
and the cognitive states of the authors such as 
%such as the sentiment of the text \cite{Davidov:2010}, its level of sarcasm \cite{Tsur:2010} and whether it's deceptive \cite{Feng:2012}.
sentiment \cite{Davidov:2010}, sarcasm \cite{Tsur:2010}, and deception \cite{Feng:2012}.  
In this paper, we study 
%to what extent is 
the extent to which people's 
writing style is affected by intricate factors, such as 
the nature of the writing task that would involve different cognitive processes.

\begin{table}[!t]
%\small
\begin{tabular}{|p{1.6cm}|p{5.3cm}|} \hline
{\bf Type} & {\bf Example} \\ \hline
{\color{blue}{\it Original}} story & My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	{\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
{\color{forestgreen}{\it Coherent}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{forestgreen}{She felt buyer's remorse after the purchase.}} \\ \hline
{\color{red}{\it Incoherent}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
\end{tabular}
\caption{\label{ROC-example}
Examples of stories from the story cloze task. The first row shows an {\it original} story written by one author. 
The second and third row show revised stories with two contrastive endings:
 %of the same story: 
 a {\it right} ending and a {\it wrong} one.
}
%\end{center}
\end{table}

%As a testbed, we experiment with
As a case study, we present experiments   based on 
the recently introduced ROC story cloze task \cite{Mostafazadeh:2016}. 
In this task, crowdsourced authors were asked to write five-sentence self-contained stories, henceforth {\it original} stories.
%Following, 
Then, 
%the stories were given to other authors, 
each original story was given to a different author, 
who was shown only the first four sentences as a story context, 
and asked to write contrastive story endings: a {\it right} (coherent) ending, and a {\it wrong} (incoherent) ending. 
%The goal of the task is to determine which of the endings is the correct one.
Framed as a story cloze task, the goal of this dataset was to serve as a commonsense challenge. 
\tabref{ROC-example} shows an example of an {\it original} story, a {\it coherent} story and an {\it incoherent} story.

While originally designed to be 
%a machine reading task, 
a commonsense story understanding challenge, 
%the compilation of this task 
the annotation process  
%raises several research questions
triggers interesting questions 
%which seem to differ from the original intent of the designers.
that may go beyond the original intent of the designers.
First, do 
%authors use different
people maintain the same writing 
style when asked to write  
%a {\it right} ending, compared to a {\it wrong} ending?
both coherent and incoherent story endings? Second, do people  
%use different style when composing the final sentence as part of their own five sentence story, compared to reading four sentences, and then writing a standalone ({\it right}) ending?
maintain the same writing style when writing the entire story on their own compared to 
writing only the final sentence for a given story context written by someone else?

%Our analysis indicates that the answer to both questions is positive. 
Our analysis indicates that different framings of similar writing tasks 
can lead to measurable differences in people's writing style.
%We experiment with a linear classifier, using simple stylistic features, such as sentence length, character n-grams and word n-grams. 
%First, we show that on a balanced dataset (chance level is 50\%) our classifier distinguishes between the {\it right} and {\it wrong} endings in 64.5\% of the cases. 
Using a simple classifier informed with stylistic features, we show that our classifier can distinguish the {\it right} and {\it wrong} endings with 64.5\% accuracy, even without looking at the story context, where chance performance is 50\%.
%It is also trained on a set of positive samples and a set of negative ones, rather than pairs of (positive, negative) pairs, as in the original story cloze task.
%Second, when trained to distinguish between the {\it original} endings and the new ({\it right}) endings, the classifier obtains 68.5\% accuracy. 
Further, our classifier can also distinguish between the {\it original} endings and the new ({\it right}) endings with 68.5\% accuracy, again without looking at the story context.

%Importantly, in both experiments, the classifier uses {\bf only} the 
%last sentence of each of the stories, and does not consider the first four sentences.
%final sentence without the story context.

In order to further estimate the quality of our results, we 
%turn back to the story cloze task.
also directly tackle the story cloze challenge. 
Adapting our classifier to the task, we obtain 72.4\% accuracy, a 12.5\% increase 
%compared to the published state-of-the-art results 
over previously reported state-of-the-art 
\cite{Salle:2016}.
%When analyzing the results of our classifier, we see that sentiment plays a significant role in its success, which suggests that constraining authors to ``wrong'' sentences results in negative text.
Our analysis reveals that sentiment plays a significant role, such that authors writing the wrong endings often engage negative sentiment.

Finally, we show that the style differences captured by our model can be combined with 
%a state-of-the-art machine reading tool, for which this task was designed, in order to obtain increased performance on the story cloze task.  
neural language models to make a better use of the story context. 
%We train a neural language model on the {\it original} five sentence training corpus, and then compute the language probability of each of the candidate endings. 
%We add the resulting probabilities as features in our linear classifier, and get 
Our final model that combines context with stylistic features achieves 
an additional 2.8\% gain -- 75.2\% -- which is 15.3\% better than the best published result.\footnote{Recently, a shared task for the story cloze task has been published (\url{https://competitions.codalab.org/competitions/15333}). At the time of submission, the leading results was 71.1\%,
%, which is  closer to our results, although still inferior.
%No details about the validity of this result or the methods used to generate it are available.
but no details are available for their results. 
}
%For instance, one of the key features for distinguishing between correct and wrong sentences is the over-representation of the word ``hate" in the latter.

\com{Our results suggest that writing style is affected by the the writer's state of mind.
Writing a sentence intended to be {\it wrong} turns out quite differently than a sentence intended to be {\it right}. 
Similarly, writing a sentence as part of the story is different from reading a story, and then writing the final sentence.}

%Our results may have a wide impact on a range of fields. 
The contributions of our study are threefold. 
First, findings from our study can potentially shed light on 
%cognitive processes that take place in the brain during writing.
how different cognitive overloads influence the style of language people use in writing. 
%Second, our results might have a more practical value in an era when fake news are becoming prominent,
%as they suggest that these might have different style compared to real news.
Second, our results provide valuable lessons for designing new NLP tasks,
both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
%Although \cite{Mostafazadeh:2016} seem to have put a lot of effort into designing the task, 
%addressing many potential methodological flaws (see \secref{ROC_Story}), the importance of a few allegedly minor details were underestimated. 
%We show that these details are actually very significant. 
Third, we establish a new state-of-the-art result on the commonsense story cloze challenge.

The remainder of this paper is organized as follows. In \secref{ROC_Story} we describe the story cloze task.
We then present our model, experiments and results in sections \ref{ssec:Model}, \ref{ssec:Experiments} and \ref{ssec:Results} respectively.
Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present an ablation study and a discussion, followed by related work in  \secref{Related}. 
We conclude at \secref{Conclusion}.

\isection{The Cloze Story Task}{ROC_Story}
In this paper, we seek to understand how different writing tasks affect writing style.
To do so, we focus on the \textit{Story Cloze Task} \cite{Mostafazadeh:2016}. 
While this task was developed to facilitate representation and learning of commonsense story understanding,
it introduces a few interesting properties which make it ideal for our study. 
We describe the task below.

@@

The ROC Story Corpus consists of 49,255 five-sentence commonsense stories, collected on Amazon Mechanical Turk (AMT).\footnote{Recently, an additional 53K stories were released, which results in roughly 100K stories.}
Workers were instructed to write a coherent self-contained story, which has a clear beginning and end. 
To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories,
which resulted in a wide range of different topics.

\paragraph{Story Cloze Task.}
After compiling the story corpus, the {\it Story Cloze Task} -- a task based on the corpus -- was introduced.
A subset of the stories was selected, and only the first four sentences of each story were presented to AMT workers.
Workers were asked to write a pair of new story endings for each story context: one {\it right} and one {\it wrong}.
Both endings are required to complete the story using one of the characters in the story context. 
Additionally,  the ending is required to be ``realistic and sensible'' \cite{Mostafazadeh:2016} when read out of context.

The resulting stories, both {\it right} and {\it wrong}, were then individually rated for coherence and meaningfulness. 
Only stories rated as simultaneously coherent with a {\it right} ending and neutral with a {\it wrong} ending were selected for the task. 
It is worth noting that workers rated the stories as a whole, not only the endings.

Based on the new stories, \citet{Mostafazadeh:2016} proposed the {\it Story Cloze Task}. 
The task is simple -- given a pair of stories that differ only in their endings, the system is required to determine which ending is {\it right} and which is {\it wrong}. 
%The authors published the ROC story corpus as the training data, and the task composed of development and test sets for which both {\it right} and {\it wrong} endings are found. 
The official training data contains only the original stories (without alternative endings), while development and test data consist only of the revised stories with alternative endings (for a different set of original stories that are included in the training set). 
The task was suggested as an extensive evaluation framework:
%as a machine reading task, 
as a commonsense story understanding task, 
as the shared task for the  Linking Models of Lexical, Sentential and Discourse-level Semantics workshop (LSDSem 2017), and as a testbed for vector-space evaluation \cite{mostafazadeh2016story}.

\paragraph{State-of-the-Art Performance.}
Interestingly, at the time of submission, 10 months after the paper was first published, the published benchmark on this task is still below 60\% \cite{Salle:2016}.\footnote{The LSDSem`17 shared task website does report higher results (71.1\%), which are still unpublished.}
This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SQuAD \cite{rajpurkar2016squad} and SNLI \cite{bowman2015large}, for which results improved dramatically over a similar period of time.
This suggest that this task is challenging and that high performance is hard to achieve.
\yc{SQuAD was officially published in Nov 2016. by the time the official EMNLP talk was presented, the leaderboard performance (still unpublished) was  30\% beyond the best results in the paper. Given that, the statement of this paragraph seems a bit of overkill...?}

@@

Despite these efforts, several key aspects were not controlled for. 
First, the training set for the task (ROC Stories corpus) is not really a training set, as it contains only positive ({\it right}) samples, and not negative ({\it wrong}) ones. 
\yc{As far as I understand, this was intentional --- they didn't want people to pick up on random superfluous cues that can inevidently get into the data creation process, exactly the kind that our work picks up. Given that, stating this can be viewed as misunderstanding, I'm afraid.}

On top of that, the {\it original} endings, which serve as positive training samples, were generated differently from the {\it right} samples, which serve as the positive samples in the development and test sets. 
While the former are part of a single coherent story written by the same author, the latter were generated by letting an author read four sentences, 
and then asking her to generate a fifth {\it right} ending. 
This raises the question of whether these different writing setups impose different writing styles. 
We show that this is indeed the case.

Second, although the {\it right} and {\it wrong} sentences were generated by the same author, 
the tasks for generating them were quite different: in one case, the author was asked to write a {\it right} ending, which would create a coherent five-sentence story along with the other four sentences. In the other case, the author was asked to write a {\it wrong} ending, which would result in an incoherent five-sentence story. 
In this work, we show that these differences are significant and impose different writing styles on authors.

\paragraph{Initial Analysis.}
We computed several characteristics of the three types of endings: {\it original} endings (from the ROC Story Corpus training set), {\it right} endings and {\it wrong} endings (both from the story cloze task development set).
Our analysis  reveals several style differences between different groups. 
First, {\it original} endings are on average much longer (11 words per sentence) than {\it right} endings (8.75 words), which are in turn also longer (though not as much)  than {\it wrong} ones (8.47 words). 
\yc{Is there psycholinguistic literature that we can cite that may have shown that cognitive burden causes writers to write shorter sentences...?}
Second, \figref{roc_pos_distribution} shows the distribution of five frequent POS tags in all three groups. 
The figure shows that both {\it original} and {\it right} endings use pronouns more frequently than {\it wrong} endings,
which in turn prefer proper nouns, especially compared to {\it original} endings.
\yc{Is there literature that may have shown that (1) pronouns correlate with coherent text, and/or (2) referencing characters by proper nouns shows a way of cognitive distancing...?}

Finally, \figref{roc_word_distribution} presents the distribution of five frequent words across the different groups. 
The figure shows that {\it original} endings prefer to use coordinations (``and'') more than  {\it right} endings, and substantially more than {\it wrong} ones.
Furthermore, {\it original} and {\it right} endings seem to prefer positive words (e.g., ``better''), while {\it wrong} endings prefer negative ones (``hates''). 
\yc{Again, any cogsci literature on this?}
Next we show that these style differences are not anecdotic, but can be used to distinguish between the different groups of text.

@@

\begin{figure*}[t!]
\begin{subfigure}{.5\textwidth}
\begin{tikzpicture}
\small
    \begin{axis}[
        width  = 0.4*\textwidth,
        height = 4cm,
      %  major x tick style = transparent,
        ybar=\pgflinewidth,
        x=2.5cm,
       bar width=5pt,
        ymajorgrids = true,
        ylabel = {Frequency in Corpus (\%)},
        symbolic x coords={{\it Original}, {\it right}, {\it Wrong}},
        xtick = data,
        scaled y ticks = false,
        %enlarge x limits=0.25,
        ymin=3,
        legend cell align=left,
        legend style={
        		legend columns=-1,
                at={(1,1.05)},
                anchor=south east,
                column sep=1ex
        }
    ]
        \addplot[style={bblue,fill=bblue,mark=none}]
            coordinates {({\it Original}, 15.3) ({\it right}, 15.7) ({\it Wrong}, 16.3)};

        \addplot[style={rred,fill=rred,mark=none}]
            coordinates {({\it Original}, 13.4) ({\it right}, 15.8) ({\it Wrong}, 15.1)};

        \addplot[style={ggreen,fill=ggreen,mark=none}]
            coordinates {({\it Original}, 10.1) ({\it right}, 9.7) ({\it Wrong}, 7.4)};

        \addplot[style={brown,fill=brown,mark=none}]
            coordinates {({\it Original}, 9.1) ({\it right}, 9.7) ({\it Wrong}, 9.4)};

        \addplot[style={gray,fill=gray,mark=none}]
            coordinates {({\it Original}, 4.7) ({\it right}, 8.3) ({\it Wrong}, 9.5)};

        \legend{NN, VBD, PRP, DT, NNP}
    \end{axis}
\end{tikzpicture}
\caption{\label{roc_pos_distribution}PoS tags}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
\begin{tikzpicture}
\small
    \begin{axis}[
        width  = 0.4*\textwidth,
        height = 4cm,
      %  major x tick style = transparent,
        ybar=\pgflinewidth,
        x=2.5cm,
       bar width=5pt,
        ymajorgrids = true,
%        ylabel = {Frequency in Corpus (\%)},
        symbolic x coords={{\it Original}, {\it right}, {\it Wrong}},
        xtick = data,
        scaled y ticks = false,
        %enlarge x limits=0.25,
        ymin=0,
        legend cell align=left,
        legend style={
        		legend columns=-1,
                at={(1,1.05)},
                anchor=south east,
                column sep=1ex
        }
    ]
        \addplot[style={bblue,fill=bblue,mark=none}]
            coordinates {({\it Original}, 3.4) ({\it right}, 3.9) ({\it Wrong}, 4)};

        \addplot[style={rred,fill=rred,mark=none}]
            coordinates {({\it Original}, 2.8) ({\it right}, 2) ({\it Wrong}, 1.5)};

        \addplot[style={ggreen,fill=ggreen,mark=none}]
            coordinates {({\it Original}, 1.1) ({\it right}, 1.4) ({\it Wrong}, 1.6)};

        \addplot[style={brown,fill=brown,mark=none}]
            coordinates {({\it Original}, 0) ({\it right}, 0) ({\it Wrong}, 0.7)};

        \addplot[style={gray,fill=gray,mark=none}]
            coordinates {({\it Original}, 0.1) ({\it right}, 0.2) ({\it Wrong}, 0)};

        \legend{to, and, I, hates, better}
    \end{axis}
\end{tikzpicture}
\caption{\label{roc_word_distribution}Words}
\end{subfigure}
\caption{The distribution of five frequent POS tags (\ref{roc_pos_distribution}) and words (\ref{roc_word_distribution})  across different endings: {\it Original} -- endings of stories from the ROC story corpus (the story cloze training set). {\it right} -- correct endings, {\it Wrong} -- wrong endings (both from story cloze task).}

@@

The goal of this paper is to determine the extent to which 
%does constraining authors in their writing assignments lead to them adopting different writing styles. 
different writing constraints lead the authors to adopt different writing styles. 
In order to answer these questions, we use simple, classic NLP tools, which have been shown to be very effective for recognizing style (see \secref{Related}).
We describe our model below.

@@

\isectionb{Experiments}
We design two experiments to answer our research questions. 
The first is an attempt to distinguish between the {\it right} and {\it wrong} endings.
The second attempts to distinguish between the {\it original} endings and new ({\it right}) endings.
We describe both experiments below.
